An In-Cloud Backup System With Deduplication for VM Snapshot

### 2012-09-14 snapshot_system/delete.tex
add pdf
add snapshot system introduction

The design goal of fuzzy deletion is to reduce the frequency of running accurate deletion.
For one VM's snapshots, let $D_{leakage}$ be the amount of storage leakage, $D_{del}$ be the average amount of data
to be deleted in one snapshot deletion, 
then we have:
\begin{equation}
D_{leakage} = N_{fuzzy} * P_{bl} * D_{del}
\end{equation}
where $N_{fuzzy}$ is the number of runs of fuzzy deletion. 
An accurate deletion is triggered to fix the storage leakage
when $D_{leakage}/D_{del}$ is accmulated to exceed certain threshold $T$:
\begin{equation}
D_{leakage} / D_{del} = N_{fuzzy} * P_{bl} > T \Rightarrow N_{fuzzy} > T/P_{bl}
\end{equation}
Therefore, when $P_{bl} = 0.01$ and $T=1$, 
there would be a run of accurate deletion for every $T/P_{bl} = 100$ runs of fuzzy deletion.
On a machine that hosts 20 VMs and each VM deletes snapshot daily, there would be less than
one accurate deletion executed per day.

\subsection{Discussion}
When a snapshot is scheduled for deletion, we always choose fuzzy deletion.

>>>>

The design goal of fuzzy deletion is to reduce the frequency of running accurate deletion.
For one VM's snapshots, let $D_{leakage}$ be the amount of storage leakage, $D_{del}$ be the average amount of data
to be deleted in one snapshot deletion, 
then we have:
\begin{equation}
D_{leakage} = N_{fuzzy} * P_{bl} * D_{del}
\end{equation}
where $N_{fuzzy}$ is the number of runs of fuzzy deletion. 
An accurate deletion is triggered to fix the storage leakage
when $D_{leakage}/D_{del}$ is accmulated to exceed certain threshold $T$:
\begin{equation}
D_{leakage} / D_{del} = N_{fuzzy} * P_{bl} > T \Rightarrow N_{fuzzy} > T/P_{bl}
\end{equation}
Therefore, when $P_{bl} = 0.01$ and $T=1$, 
there would be a run of accurate deletion for every $T/P_{bl} = 100$ runs of fuzzy deletion.
On a machine that hosts 20 VMs and each VM deletes snapshot daily, there would be less than
one accurate deletion scheduled per day.

\subsection{Discussion}
